\documentclass[11pt]{article}
\usepackage[latin2]{inputenc}
\usepackage{a4wide}
\usepackage{graphicx}
\title{Prusa Mendel documentation}
\author{ThingDoc 2011/05/30 05:54:16}
\begin{document}
\maketitle
Prusa Mendel is machine from RepRap project. RepRap is open source 3D printer.
\newpage
\tableofcontents
\newpage
\section{Bill of materials}
List of things you need to build the machine divided by categories
\subsection{Rods and Bars}
\begin{itemize}
\item 1x Idler
\end{itemize}
\subsection{Nuts\&bolts}
\begin{itemize}
\item 3x 608 skate bearing
\item 4x M4 nut
\item 3x M3 10mm screw
\item 2x M4 25mm screw
\item 2x M3 25mm screw with HEX head
\item 2x M3 15mm screw with HEX head
\item 2x M3 10mm screw with hex head
\item 1x M3 25mm screw
\item 1x M8 hobbed bolt
\item 1x M3 grub screw
\item 17x M3 washer
\item 37x M8 washer
\item 38x M8 nut
\item 6x M3 nut
\item 1x M3 10mm screw with flat head
\item 2x M3 40mm screw
\end{itemize}
\subsection{Printed}
\begin{itemize}
\item 1x Extruder body
\item 16x Bar clamp
\item 4x Y bushing
\item 4x Frame vertex
\item 1x Large extruder gear
\item 1x Small extruder gear
\item 2x Rod clamp
\item 4x Frame vertex with foot
\item 1x Y motor bracket
\item 2x Belt clamp
\item 1x X carriage
\item 1x Z motor mount
\item 1x Extruder Idler
\end{itemize}
\newpage
\section{Things overview}
List of things and their descriptions
\subsection{Y axis}
Assembled Y axis

\subsection{Frame with axes}
Frame with all axes mounted

\subsection{Frame vertex}

\subsection{Frame}
Frame for adding all of the other parts

\subsection{load tester}

\subsection{Y motor bracket}

\subsection{M8 hobbed bolt}

\subsection{Extruder Idler}
Extruder idler

\subsection{Frame with Y axis}
Frame with Y axis mounted

\subsection{Y bushing}

\subsection{Bar clamp}

\subsection{Configuration test}

\subsection{XZ axis}
Assembled XZ axis

\subsection{Large extruder gear}

\subsection{Frame vertex with foot}

\subsection{X end motor}

\subsection{Extruder body}
Extruder body

\subsection{Small extruder gear}

\subsection{Extruder spring}
Spring used for idler on extruder.

\subsection{Printable Bushing}

\subsection{X carriage}

\subsection{X end idler}

\subsection{Rod clamp}

\subsection{Z motor mount}

\subsection{Endstop holder}

\subsection{Bushing}

\subsection{Idler}
Small M8 rod

\subsection{Pulley}

\subsection{Coupling}

\subsection{Carriage}
X-carriage with mounted extruder

\subsection{Belt clamp}

\subsection{Extruder}
Extruder 
 
 

\newpage
\section{Assembly instructions}
\subsection{Assemble Small extruder gear}
\begin{itemize}
\item Insert nut into cavity in printed gear.
\item Tighten the grub screw a bit, just to hold in place.
\end{itemize}
\subsection{Assemble Extruder Idler}
\begin{itemize}
\item Insert piece of M8 rod into bearing.
\item Insert 608 bearing with rod into printed idler part.
\end{itemize}
\subsection{Assemble M8 hobbed bolt}
\begin{itemize}
\item Use thread cutting bit in electric screwdriver ...
\end{itemize}
\subsection{Assemble Large extruder gear}
\begin{itemize}
\item Insert hobbed bolt into main hole.
\item Add some M8 washers from other side, later with their count you adjust position of hobbed part in filament path.
\end{itemize}
\subsection{Assemble Extruder}
\begin{itemize}
\item Take idler and insert nut into small nut-trap inside the hinge.
\item While holding the nut in place, preprare M3x25 bolt with washer and screw it into the hinge just enough to hold the nut.
\item Now take the extruder body and idler. Place idler on the hinge counterpart and compleately screw the M3x25 bolt. This will create secured hinge.
\item Place M4 nuts into their nut traps, secure them with piece of tape. We need them in place, since later they would be harder to access.
\item Prepare your NEMA17 stepper motor and three M3x10 screws with washers.
\item Hold motor on place and lightly tighten the screws. We need to adjust motor position later, no need to tighten it hard.
\item Place two skate bearings on ther position, they should snuggly fit in.
\item Insert prepared large gear into the body with mounted bearings.
\item Check if the alignment of hobbed part with the filament path. Adjust it accordingly with adding or removing M8 washers.
\item After adjusting, we need to fix the bolt in. So we place washer at the end of hobbed bolt and with two M8 nuts we will do locknut by tightening them against each other.
\item Check if large gear turns freely.
\item Prepare two M3x40 screws with sandwitch of washer-spring-washer.
\item Insert two M3 nuts into nut traps on top of drive mechanism.
\item Insert prepared screws into the holes on idler. Close the idler and tighten the screws into the trapped nuts. More you tighten those screws, more pressure will be on fillament.
\item Your extruder is done.
\end{itemize}
\newpage
\end{document}
